upwell_IDX

### 2019-08-27 SST_patterns.Rmd
Updated

```{r}
# SACTN_US <- SACTN_US %>% 
#   dplyr::rename(in_situ_temp = temp)
# 
# # Visualising the data
# temp_plot <- function(df){
#   plot <- ggplot(data = df, aes(x = date, y = in_situ_temp, colour = site)) +
#     geom_line(aes(group = site)) +
#     labs(x = "", y = "Temperature (°C)") +
#     theme(axis.text.x = element_text(angle = 45)) +
#     theme(legend.position = "top")
# }
# 
# SACTN_plot <- temp_plot(df = SACTN_US)
# SACTN_plot
```

@@

```{r}
# load("Data/site_list_sub.Rdata")
# # xtable(site_list_sub, auto = TRUE)
# west <- site_list_sub
# west$coast <- "west" # Chnages wc to west
# 
# load("Data/africa_coast.RData")
# 
# ## Downloading the bathy data from NOAA
# # Download mid-res bathymetry data
# # sa_lat <- c(-38, -24.5); sa_lon <- c(11.5, 35.5)
# # sa_bathy <- as.xyz(getNOAA.bathy(lon1 = sa_lon[1], lon2 = sa_lon[2], lat1 = sa_lat[1], lat2 = sa_lat[2], resolution = 4))
# # colnames(sa_bathy) <- c("lon", "lat", "depth")
# # sa_bathy <- sa_bathy[sa_bathy$depth <= 0,]
# # save(sa_bathy, file = "Data_P1/bathy/sa_bathy.RData")
# 
# # Loading in the newly downloaded bathymetry data
# load("Data/bathy/sa_bathy.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# shore.normal.transect <- function(site, width = 2){
#   # Find the site on the coastline and it's nearest neighbour points
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   coords2 <- knnx.index(africa_coast[,1:2], as.matrix(coords), k = 1)
#   coords3 <- data.frame(site = site$site, africa_coast[c(coords2-width, coords2+width),]) 
#   coords3 <- coords3[2:1,1:3]
#   # Define the shore normal transect bearing
#   heading <- earth.bear(coords3[1,2], coords3[1,3], coords3[2,2], coords3[2,3]) + 90
#   if(heading >= 360){
#     heading <- heading-360
#   } else {
#     heading <- heading
#   }
#   heading2 <- data.frame(site = site$site, lon = site$lon, lat = site$lat, heading)
#   return(heading2)
# }
# 
# # Creating the transects
# site_transects <- data.frame()
# for(i in 1:length(west$site)){
#  site <- west[i,]
#  site_transect <- shore.normal.transect(site, 2)
#  site_transects <- rbind(site_transects, site_transect)
# }
# 
# # Manually correcting Sea Point and Kommetjie
# site_transects$heading[4:5] <- 290 
# # save(site_transects, file = "Data/site_transects.RData")
# load("Data/site_transects.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# # It then extracts a lat/ lon point every X kilometres until reaching a specified isobath
# 
# transect.pixel <- function(site, distances){
#   # Extract coordinates
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   # Find lon/ lats every X metres 
#   pixels <- data.frame()
#   # deep <- 999
#   # distance_multiplier <- 1
#   # while(deep > isobath){
#   for(i in 1:length(distances)){
#     coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
#     sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
#     bathy2 <- sa_bathy[sitesIdx,]
#     bathy2 <- bathy2[complete.cases(bathy2$depth),]
#     bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
#                          heading = site$heading, 
#                          distance = distances[i])
#     pixels <- rbind(pixels, bathy3)
#     coords <- coords2
#   }
#   if(nrow(pixels) < 1){
#     pixels <- data.frame(site, depth = NA)
#   }else{
#     pixels <- pixels
#   }
#   return(pixels)
# }
# 
# # Pixel points
# site_pixels <- data.frame()
# for(i in 1:length(west$site)){
#   site <- site_transects[i,]
#   site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
#   site_pixels <- rbind(site_pixels, site_pixel)
# }
# 
# # Bounding box
#   # Only one is made in order to know how large the the geom_point() squares should be made to match
# bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
#                    xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
#                    ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
#                    ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
# 
# # Determining the temperature at the various distances from the coast
# 
# # save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")
```

@@

>>>>

```{r}
# SACTN_US <- SACTN_US %>% 
#   dplyr::rename(in_situ_temp = temp)
# 
# # Visualising the data
# temp_plot <- function(df){
#   plot <- ggplot(data = df, aes(x = date, y = in_situ_temp, colour = site)) +
#     geom_line(aes(group = site)) +
#     labs(x = "", y = "Temperature (°C)") +
#     theme(axis.text.x = element_text(angle = 45)) +
#     theme(legend.position = "top")
# }
# 
# SACTN_plot <- temp_plot(df = SACTN_US)
# SACTN_plot

# 25th quantile
```

@@

```{r}
# load("Data/site_list_sub.Rdata")
# # xtable(site_list_sub, auto = TRUE)
# west <- site_list_sub
# west$coast <- "west" # Chnages wc to west
# 
# load("Data/africa_coast.RData")
# 
# ## Downloading the bathy data from NOAA
# # Download mid-res bathymetry data
# # sa_lat <- c(-38, -24.5); sa_lon <- c(11.5, 35.5)
# # sa_bathy <- as.xyz(getNOAA.bathy(lon1 = sa_lon[1], lon2 = sa_lon[2], lat1 = sa_lat[1], lat2 = sa_lat[2], resolution = 4))
# # colnames(sa_bathy) <- c("lon", "lat", "depth")
# # sa_bathy <- sa_bathy[sa_bathy$depth <= 0,]
# # save(sa_bathy, file = "Data_P1/bathy/sa_bathy.RData")
# 
# # Loading in the newly downloaded bathymetry data
# load("Data/bathy/sa_bathy.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# shore.normal.transect <- function(site, width = 2){
#   # Find the site on the coastline and it's nearest neighbour points
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   coords2 <- knnx.index(africa_coast[,1:2], as.matrix(coords), k = 1)
#   coords3 <- data.frame(site = site$site, africa_coast[c(coords2-width, coords2+width),]) 
#   coords3 <- coords3[2:1,1:3]
#   # Define the shore normal transect bearing
#   heading <- earth.bear(coords3[1,2], coords3[1,3], coords3[2,2], coords3[2,3]) + 90
#   if(heading >= 360){
#     heading <- heading-360
#   } else {
#     heading <- heading
#   }
#   heading2 <- data.frame(site = site$site, lon = site$lon, lat = site$lat, heading)
#   return(heading2)
# }
# 
# # Creating the transects
# site_transects <- data.frame()
# for(i in 1:length(west$site)){
#  site <- west[i,]
#  site_transect <- shore.normal.transect(site, 2)
#  site_transects <- rbind(site_transects, site_transect)
# }
# 
# # Manually correcting Sea Point and Kommetjie
# site_transects$heading[4:5] <- 290 
# # save(site_transects, file = "Data/site_transects.RData")
# load("Data/site_transects.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# # It then extracts a lat/ lon point every X kilometres until reaching a specified isobath
# 
# transect.pixel <- function(site, distances){
#   # Extract coordinates
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   # Find lon/ lats every X metres 
#   pixels <- data.frame()
#   # deep <- 999
#   # distance_multiplier <- 1
#   # while(deep > isobath){
#   for(i in 1:length(distances)){
#     coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
#     sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
#     bathy2 <- sa_bathy[sitesIdx,]
#     bathy2 <- bathy2[complete.cases(bathy2$depth),]
#     bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
#                          heading = site$heading, 
#                          distance = distances[i])
#     pixels <- rbind(pixels, bathy3)
#     coords <- coords2
#   }
#   if(nrow(pixels) < 1){
#     pixels <- data.frame(site, depth = NA)
#   }else{
#     pixels <- pixels
#   }+

#   return(pixels)
# }
# 
# # Pixel points
# site_pixels <- data.frame()
# for(i in 1:length(west$site)){
#   site <- site_transects[i,]
#   site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
#   site_pixels <- rbind(site_pixels, site_pixel)
# }
# 
# # Bounding box
#   # Only one is made in order to know how large the the geom_point() squares should be made to match
# bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
#                    xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
#                    ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
#                    ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
# 
# # Determining the temperature at the various distances from the coast
# 
# # save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")
```

@@

## Function
Determining the temperatures at the various distances from the coastline

```{r}
# Splitting the dataset

PN_site <- site_pixels %>% 
  filter(site == "Port Nolloth")

LB_site <- site_pixels %>% 
  filter(site == "Lamberts Bay")

SB_site <- site_pixels %>% 
  filter(site == "Saldanha Bay")

SP_site <- site_pixels %>% 
  filter(site == "Sea Point")

HB_site <- site_pixels %>% 
  filter(site == "Hout Bay")

## Functions:

MUR <- MUR %>% 
  select(site, lon, lat, temp.y)

OISST <- OISST %>% 
  select(site, lon, lat, temp.y)

unique_pixels <- function(df){
  unique_pixel <- df %>%
  select(lon, lat) %>%
  unique()
  return(unique_pixel)
}

MUR_pixels <- unique_pixels(df = MUR)
# SACTN_pixels <- unique_pixels(df = SACTN)
OISST_pixels <- unique_pixels(df = OISST)
CMC_pixels <- unique_pixels(df = CMC)

match_func <- function(df, xy){
  match_index <- knnx.index(data = as.matrix(df[,1:2]),
                    query = as.matrix(xy[,2:3]), k = 1)
  return(match_index)
}

MUR_PN <- match_func(df = MUR_pixels, xy = PN_site)
MUR_LB <- match_func(df = MUR_pixels, xy = LB_site)
MUR_SB <- match_func(df = MUR_pixels, xy = SB_site)
MUR_SP <- match_func(df = MUR_pixels, xy = SP_site)
MUR_HB <- match_func(df = MUR_pixels, xy = HB_site)

# SACTN_pixels <- match_func(df = SACTN)
OISST_PN <- match_func(df = OISST_pixels, xy = PN_site)
OISST_LB <- match_func(df = OISST_pixels, xy = LB_site)
OISST_SB <- match_func(df = OISST_pixels, xy = SB_site)
OISST_SP <- match_func(df = OISST_pixels, xy = SP_site)
OISST_HB <- match_func(df = OISST_pixels, xy = HB_site)

CMC_PN <- match_func(df = CMC_pixels, xy = PN_site)
CMC_LB <- match_func(df = CMC_pixels, xy = LB_site)
CMC_SB <- match_func(df = CMC_pixels, xy = SB_site)
CMC_SP <- match_func(df = CMC_pixels, xy = SP_site)
CMC_HB <- match_func(df = CMC_pixels, xy = HB_site)

pixel_match_func <- function(df, xy){ 
  pixel_match <- df[xy,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = PN_site$site)
  return(pixel_match)
}

MUR_match_PN <- pixel_match_func(df = MUR_pixels, xy = MUR_PN)
MUR_match_LB <- pixel_match_func(df = MUR_pixels, xy = MUR_LB)
MUR_match_SB <- pixel_match_func(df = MUR_pixels, xy = MUR_SB)
MUR_match_SP <- pixel_match_func(df = MUR_pixels, xy = MUR_SP)
MUR_match_HB <- pixel_match_func(df = MUR_pixels, xy = MUR_HB)

CMC_match_PN <- pixel_match_func(df = CMC_pixels, xy = CMC_PN)
CMC_match_LB <- pixel_match_func(df = CMC_pixels, xy = CMC_LB)
CMC_match_SB <- pixel_match_func(df = CMC_pixels, xy = CMC_SB)
CMC_match_SP <- pixel_match_func(df = CMC_pixels, xy = CMC_SP)
CMC_match_HB <- pixel_match_func(df = CMC_pixels, xy = CMC_HB)

OISST_match_PN <- pixel_match_func(df = OISST_pixels, xy = OISST_PN)
OISST_match_LB <- pixel_match_func(df = OISST_pixels, xy = OISST_LB)
OISST_match_SB <- pixel_match_func(df = OISST_pixels, xy = OISST_SB)
OISST_match_SP <- pixel_match_func(df = OISST_pixels, xy = OISST_SP)
OISST_match_HB <- pixel_match_func(df = OISST_pixels, xy = OISST_HB)

match_func <- function(df,xy){
matched_coords <- df %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% xy$combi)
return(matched_coords)
}

MUR_temp_PN <- match_func(df = MUR, xy = MUR_match_PN)
MUR_temp_LB <- match_func(df = MUR, xy = MUR_match_LB)
MUR_temp_SB <- match_func(df = MUR, xy = MUR_match_SB)
MUR_temp_SP <- match_func(df = MUR, xy = MUR_match_SP)
MUR_temp_HB <- match_func(df = MUR, xy = MUR_match_HB)

CMC_temp_PN <- match_func(df = CMC, xy = CMC_match_PN)
CMC_temp_LB <- match_func(df = CMC, xy = CMC_match_LB)
CMC_temp_SB <- match_func(df = CMC, xy = CMC_match_SB)
CMC_temp_SP <- match_func(df = CMC, xy = CMC_match_SP)
CMC_temp_HB <- match_func(df = CMC, xy = CMC_match_HB)
```

### 2019-08-27 upwell_IDX.Rmd
Updated

detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 3, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  # The climatology base period used here is up for debate...
  # The choice of the 30th percentile threshold also needs to be justified and sensitivty tested
  mutate(clim = purrr::map(data, ts2clm, pctile = 20, climatologyPeriod = c("1995-01-01", "2004-12-31"))) %>%
  select(-data) %>% 
  unnest() %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  # mutate(thresh = mean(seas, na.rm = T)-sd(seas, na.rm = T)) %>% # Manually set threshold to the mean
  # mutate(thresh = 10) %>% # Manually set threshold to a static value. Doesn't work across all sites
  # mutate(thresh = quantile(temp, 0.3, na.rm = T)) %>% # Manually set threshold to a single quantile
  nest() %>% 
  mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  select(-data) #%>% 
  # unnest() %>% 
  # filter(row_number() %% 2 == 0) %>% # Select event summary metrics
  # filter(row_number() %% 2 == 1) %>% # Select daily values
  # unnest()

@@

```{r}
load("Data/wind_daily.RData")

wind_daily <- wind_daily %>% 
  dplyr::rename(t = date)

# wind_daily_season <- season_func(df = wind_daily)

#save(wind_daily_season, file = "Data/wind_daily_season.RData")

load("Data/wind_daily_season.RData")

wind_daily_season_test <- wind_daily_season %>% 
  group_by(season, temp_sites) %>% 
  arrange(mean_speed) %>% 
  # Add the following line with mutate to filter the data and add a text label to use with an ANOVA
  summarize(msp_1st = quantile(mean_speed, probs=0.33, na.rm=TRUE),
            mspeed_2nd = quantile(mean_speed, probs=0.66, na.rm=TRUE))

# T-test

# T- test between seasons for all sites

```

>>>>

detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 3, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  # The climatology base period used here is up for debate...
  # The choice of the 30th percentile threshold also needs to be justified and sensitivty tested
  mutate(clim = purrr::map(data, ts2clm, pctile = 25, climatologyPeriod = c("1995-01-01", "2004-12-31"))) %>%
  select(-data) %>% 
  unnest() %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  # mutate(thresh = mean(seas, na.rm = T)-sd(seas, na.rm = T)) %>% # Manually set threshold to the mean
  # mutate(thresh = 10) %>% # Manually set threshold to a static value. Doesn't work across all sites
  # mutate(thresh = quantile(temp, 0.3, na.rm = T)) %>% # Manually set threshold to a single quantile
  nest() %>% 
  mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  select(-data) #%>% 
  # unnest() %>% 
  # filter(row_number() %% 2 == 0) %>% # Select event summary metrics
  # filter(row_number() %% 2 == 1) %>% # Select daily values
  # unnest()

@@

```{r}
# load("Data/wind_daily.RData") 
# 
# wind_daily <- wind_daily %>% 
#   dplyr::rename(t = date)
# 
# # wind_daily_season <- season_func(df = wind_daily)
# 
# #save(wind_daily_season, file = "Data/wind_daily_season.RData")
# 
# load("Data/wind_daily_season.RData")
# 
# wind_daily_season_test <- wind_daily_season %>% 
#   group_by(season, temp_sites) %>% 
#   arrange(mean_speed) %>% 
#   # Add the following line with mutate to filter the data and add a text label to use with an ANOVA
#   summarize(msp_1st = quantile(mean_speed, probs=0.33, na.rm=TRUE),
#             mspeed_2nd = quantile(mean_speed, probs=0.66, na.rm=TRUE))
```
